% FREUID Challenge 2026 — Technical Report (team jgshin22)
% Compile: tectonic freuid_technical_report.tex  (or pdflatex + bibtex)

\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}

\geometry{margin=2.5cm}
\hypersetup{colorlinks=true, linkcolor=blue!60!black, citecolor=blue!60!black, urlcolor=blue!60!black}

\newcommand{\teamname}{jgshin22}
\newcommand{\kaggleteam}{jgshin22}
\newcommand{\contactemail}{jgshin22@gmail.com}
\newcommand{\reportdate}{July 15, 2026}

\title{%
  \textbf{The FREUID Challenge 2026}\\[0.4em]
  \large Technical Report --- Template-Aligned Field-Crop MIL Forensics
}
\author{Gyucheol Shin\\ \small \texttt{\contactemail}}
\date{Report date: \reportdate}

\begin{document}
\maketitle

\begin{abstract}
We address binary detection of forged identity documents across five
template-locked document types (four driving licences, one ID card; Latin and
Arabic scripts) under the DET-based FREUID score (lower is better). Our key
observation is that all documents of a type are pixel-aligned to a common
template, while whole-image downsampling (e.g.\ to $384^2$) renders document
text $\sim$10\,px tall, making character-level tampering physically invisible
to a whole-image classifier. Our system therefore scores documents
\emph{per field}: for each type we derive up to 13 field bounding boxes
(photo, name, date fields, document number, MRZ, plus three static zones)
from per-pixel variance templates over bona-fide images, cut the crops at
native resolution, and score each crop with a shared EfficientNet-B3 fed
channel-concatenated RGB and SRM noise-residual streams. The document fraud
score is the maximum over crop scores (multiple-instance learning), with
horizontal-flip test-time augmentation. Trained only on the official training
set (ImageNet-initialised backbone), this single model improves the public
leaderboard from 0.15185 (our best whole-image baseline) to \textbf{0.03905},
a $3.9\times$ reduction. Code (MIT), frozen weights, and a no-network Docker
container reproduce the submission end-to-end.
\end{abstract}

\noindent\textbf{Competition:} The FREUID Challenge 2026 (IJCAI-ECAI 2026)\\
\textbf{Kaggle team:} \kaggleteam\\
\textbf{Code:} \url{https://github.com/sdlvkqmv/freuid-challenge-2026}\\

\section{Introduction}
\label{sec:intro}
The challenge asks for a continuous fraud score per document image; the
metric, FREUID $=1-\mathrm{HM}(1-\mathrm{AuDET},\,1-\mathrm{APCER@1\%BPCER})$,
is computed from the full DET curve, so ranking quality and the strict
1\%-BPCER operating point matter while monotonic rescaling does not. The
threat model mixes physical manipulation, generative-AI edits, and
print-and-capture recapture~\cite{freuid2026}. The central practical
difficulty is a train/test domain gap: near-perfect in-domain validation
($\sim 10^{-4}$ FREUID) coexists with public-leaderboard scores two to three
orders of magnitude worse, so local CV cannot rank candidate models.

\section{Method}
\label{sec:method}

\subsection{Overview}
Pipeline: (1) assign each test image a document type by 1024-bit
difference-hash (dhash) nearest-neighbour matching against all 69{,}352
training images (documents are template-locked, so this is near-perfect);
(2) resize to the type's canonical resolution; (3) cut $K\le 13$ predefined
field crops and resize each to $320^2$; (4) score every crop with a shared
CNN; (5) document score $=\max_k \sigma(\text{logit}_k)$, averaged over two
horizontal-flip views.

\subsection{Template-aligned field boxes}
Per type we compute per-pixel mean/standard-deviation templates over aligned
bona-fide images. High-variance pixels localise per-document ink; horizontal
dilation and vertical closing merge glyphs into field bands, and connected
components give candidate boxes. We keep the portrait photo, up to nine field
bands (name, dates, document number, MRZ, hologram areas), and three fixed
static-background zones, padded by 3\% (\texttt{assets/field\_boxes\_v2.json}).

\subsection{Model architecture}
A single EfficientNet-B3 (timm \texttt{tf\_efficientnet\_b3}, ImageNet
initialisation, $\sim$11M parameters) with 6 input channels: RGB plus a fixed
3-channel SRM high-pass noise residual (Fridrich--Kodovsk\'y kernels). The
scorer is shared across crops; a document is a bag of $K{=}13$ crop instances
(missing boxes padded by repetition) and the document logit is the max over
per-crop logits --- one tampered field suffices to make a document fraudulent.

\subsection{Training objective and procedure}
BCE-with-logits on the document logit with $\text{pos\_weight}=1.363$
(class balance); AdamW, LR $3\times10^{-4}$ with one-epoch warmup and cosine
decay, weight decay 0.05, 6 epochs, batch 3 documents (39 crops), AMP,
gradient clipping 1.0, seed 42. Augmentation: horizontal flip (p=0.5) and
ColorJitter(0.1); no random-resized-crop (it would break template alignment).
Best-validation checkpoint (epoch 4) selected.

\subsection{Score calibration}
None. Submitted scores are raw sigmoid probabilities; the metric is invariant
to monotonic transforms. A per-type rank normalisation was tried and
\emph{regressed} the leaderboard (0.571), so no post-processing is applied.

\section{Data}
\label{sec:data}

\subsection{FREUID training set}
All 69{,}352 official training images; labels from
\texttt{train\_labels.csv}. \texttt{is\_digital} is degenerate (69{,}332 of
69{,}352 True) and unused. Stratified 5-fold split by
(\texttt{label}$\times$\texttt{type}); fold 0 held out for validation.

\subsection{External data and pre-trained models}
No external data beyond FREUID and publicly licensed ImageNet-pretrained
\texttt{timm} weights (Apache-2.0), used only for backbone initialisation at
training time.

\subsection{Validation strategy}
In-domain validation saturates ($10^{-4}$--$10^{-7}$ FREUID) and does not
track the leaderboard; model selection therefore used public-leaderboard
submissions (30+ attempts over the competition).
Private test labels were never used; private-row predictions were produced
after the July 13 private release by inference with the frozen checkpoints
(v2 primary, v1 as the second Kaggle final selection; no weight, architecture,
or training-code changes).

\section{Inference}
\label{sec:inference}
Exact command (also the Docker entrypoint):
\texttt{python submission/prepare\_submission.py} with \texttt{/data} (flat
image directory) and \texttt{/submissions} mounted. Steps: dhash type
assignment $\rightarrow$ canonical resize $\rightarrow$ 13 field crops at
$320^2$ $\rightarrow$ shared scorer $\rightarrow$ hflip-TTA max-aggregation.
Batch 6 documents (78 crops); one 10\,GB GPU processes the 7{,}821 public
images in a few minutes (CPU $\sim$20--30$\times$ slower). Output:
\texttt{submission.csv} with \texttt{id,label}.

\section{Results}
\label{sec:results}

\begin{table}[h]
  \centering
  \caption{Main results. Lower FREUID is better.}
  \label{tab:results}
  \begin{tabular}{lcc}
    \toprule
    Model & Local val FREUID & Public LB FREUID \\
    \midrule
    Whole-image EffB3+SRM+recapture-aug (best of 20+ variants) & $\sim10^{-4}$ & 0.15185 \\
    Field-crop MIL v1 (K=10, 256px; second final selection) & $\sim10^{-6}$ & 0.08023 \\
    \textbf{Field-crop MIL v2 (K=13, 320px, hflip, static zones)} & $1.2\times10^{-7}$ & \textbf{0.03905} \\
    \bottomrule
  \end{tabular}
\end{table}

Notable negative results (all public-LB verified): DCT input stream, frozen
CLIP/DINOv2 probes, test-time BN adaptation, hard-negative mining, blind
multi-crop aggregation, synthetic recapture-realism augmentation,
face-consistency fusion, diverse-backbone and reseed ensembles of the
whole-image model, per-type rank normalisation. The single change that broke
the whole-image plateau was \emph{where the model looks} (native-resolution
field crops with max aggregation), not the loss, stream set, or backbone.

\section{Reproducibility}
\label{sec:repro}
\begin{itemize}[noitemsep]
  \item \textbf{Repository:} \url{https://github.com/sdlvkqmv/freuid-challenge-2026} (MIT); the frozen commit SHA is stated in our Kaggle discussion reply.
  \item \textbf{Docker:} \texttt{docker build -t freuid-repro:local -f submission/Dockerfile .} from the repo root; weights (43\,MB), field boxes, and dhash references are baked into the image (\texttt{assets/}, SHA-256 in \texttt{assets/CHECKSUMS.txt}).
  \item \textbf{Dependencies:} Python 3.11, PyTorch 2.4.1, timm 1.0.27 (pinned in \texttt{submission/requirements.txt}); CUDA 12.1 optional.
  \item \textbf{Runtime:} full public-test inference in minutes on one 10\,GB GPU; training $\sim$6\,h on the same GPU.
  \item \textbf{Randomness:} seed 42 everywhere; cuDNN autotune enabled (training non-bitwise-deterministic; the frozen checkpoint removes this concern at inference).
  \item \textbf{Network:} inference runs under \texttt{--network none}; no runtime downloads.
\end{itemize}

\section{Team and contributions}
Solo entry: Gyucheol Shin (modelling, experimentation, engineering, writing),
assisted by AI pair-programming tools for implementation and experiment
management.

\bibliographystyle{plain}
\bibliography{references}

\appendix
\section{Hyperparameters}
\label{app:hparams}
\begin{table}[h]
  \centering
  \small
  \begin{tabular}{ll}
    \toprule
    Hyperparameter & Value \\
    \midrule
    Crop size / count & $320^2$ / $K{=}13$ per document \\
    Canonical sizes & BENIN,MAURITIUS $1585{\times}1000$; EGYPT $1387{\times}875$; GUINEA $1584{\times}1000$; MOZAMBIQUE $1000{\times}630$ \\
    Batch size & 3 documents (39 crops) \\
    Learning rate & $3\times10^{-4}$, 1-epoch warmup, cosine decay \\
    Weight decay & 0.05 \\
    Epochs & 6 (best-val = epoch 4) \\
    Loss & BCE, pos\_weight 1.363 \\
    Augmentation & hflip 0.5, ColorJitter 0.1 \\
    TTA & horizontal flip (2 views) \\
    Seed & 42 \\
    \bottomrule
  \end{tabular}
\end{table}

\end{document}
